Existing Model

### 2022-02-18 DataSetup.Rmd
Added code for 2 year follow up

@@

#Create empty columns to match feature list
renamed_smri[,"FS_BrainSeg_Vol"] <- NA
renamed_smri[,"FS_BrainSeg_Vol_No_Vent"] <- NA
renamed_smri[,"FS_BrainSeg_Vol_No_Vent_Surf"] <- NA
renamed_smri[,"FS_SupraTentorial_Vol_No_Vent"] <- NA
renamed_smri[,"FS_SupraTentorial_No_Vent_Voxel_Count"] <- NA
renamed_smri[,"FS_Mask_Vol"] <- NA
renamed_smri[,"FS_BrainSegVol_eTIV_Ratio"] <- NA
renamed_smri[,"FS_MaskVol_eTIV_Ratio"] <- NA
renamed_smri[,"FS_L_Vessel_Vol"] <- NA
renamed_smri[,"FS_L_ChoroidPlexus_Vol"] <- NA
renamed_smri[,"FS_R_Vessel_Vol"] <- NA
renamed_smri[,"FS_R_ChoroidPlexus_Vol"] <- NA
renamed_smri[,"FS_OpticChiasm_Vol"] <- NA
renamed_smri[,"FS_Total_GM_Vol"] <- NA

@@

#Convert to numeric
renamed_smri[,6:279] <- sapply(renamed_smri[,6:279],as.numeric)
renamed_smri <- renamed_smri %>% 
  mutate(interview_age = as.numeric(interview_age)/12)

>>>>

smri_followup <- smri_1%>% 
  filter(eventname=="2_year_follow_up_y_arm_1")

@@

#Create empty columns to match feature list
renamed_smri_followup[,"FS_BrainSeg_Vol"] <- NA
renamed_smri_followup[,"FS_BrainSeg_Vol_No_Vent"] <- NA
renamed_smri_followup[,"FS_BrainSeg_Vol_No_Vent_Surf"] <- NA
renamed_smri_followup[,"FS_SupraTentorial_Vol_No_Vent"] <- NA
renamed_smri_followup[,"FS_SupraTentorial_No_Vent_Voxel_Count"] <- NA
renamed_smri_followup[,"FS_Mask_Vol"] <- NA
renamed_smri_followup[,"FS_BrainSegVol_eTIV_Ratio"] <- NA
renamed_smri_followup[,"FS_MaskVol_eTIV_Ratio"] <- NA
renamed_smri_followup[,"FS_L_Vessel_Vol"] <- NA
renamed_smri_followup[,"FS_L_ChoroidPlexus_Vol"] <- NA
renamed_smri_followup[,"FS_R_Vessel_Vol"] <- NA
renamed_smri_followup[,"FS_R_ChoroidPlexus_Vol"] <- NA
renamed_smri_followup[,"FS_OpticChiasm_Vol"] <- NA
renamed_smri_followup[,"FS_Total_GM_Vol"] <- NA

@@

#Convert to numeric
renamed_smri_followup[,6:279] <- sapply(renamed_smri_followup[,6:279],as.numeric)
renamed_smri_followup <- renamed_smri_followup %>% 
  mutate(interview_age = as.numeric(interview_age)/12)

### 2022-02-18 ExisitingModel.Rmd
Added code for 2 year follow up

Predict Brain Age
```{r}
brain_age_df <-
  xgb_mod %>%
  predict(new_data = renamed_smri) %>%
  mutate(
    # provide the chronological age at time of scan
    truth = renamed_smri$interview_age
  ) %>%
  # compute the brain age gap by subtracting chronological age from prediction
  mutate(gap = .pred - truth)
```

Evaluate accuracy
```{r}
# compute common performance metrics: mae, rsq, rmse
brain_age_df %>%
  metrics(truth = truth, estimate = .pred)
```

@@

@@

@@

@@

ggplot(as.data.frame(brain_age_corrected_df), aes(x=corrected_pred)) +
  geom_histogram()
```

>>>>

Predict Brain Age
```{r}
brain_age_df <-
  xgb_mod %>%
  predict(new_data = renamed_smri) %>%
  mutate(
    # provide the chronological age at time of scan
    truth = renamed_smri$interview_age
  ) %>%
  # compute the brain age gap by subtracting chronological age from prediction
  mutate(gap = .pred - truth)

brain_age_df_followup <-
  xgb_mod %>%
  predict(new_data = renamed_smri_followup) %>%
  mutate(
    # provide the chronological age at time of scan
    truth = renamed_smri_followup$interview_age
  ) %>%
  # compute the brain age gap by subtracting chronological age from prediction
  mutate(gap = .pred - truth)
```

Evaluate accuracy
```{r}
# compute common performance metrics: mae, rsq, rmse
brain_age_df %>%
  metrics(truth = truth, estimate = .pred)

brain_age_df_followup %>%
  metrics(truth = truth, estimate = .pred)
```

@@

brain_age_corrected_df_followup <- brain_age_df_followup %>%
  mutate(
    # corrected brain age prediction
    corrected_pred =  (.pred - bias_intercept) / bias_slope
  ) %>%
  # corrected corrected brain age gap
  mutate(corrected_gap = corrected_pred - truth)

@@

brain_age_corrected_df_followup %>%
  metrics(truth = truth, estimate = corrected_pred)

save(brain_age_df, file="BaselineBrainAge.Rda")
save(brain_age_corrected_df, file="BaselineBrainAgeCorrected.Rda")

save(brain_age_df_followup, file="FollowUpBrainAge.Rda")
save(brain_age_corrected_df_followup, file="FollowUpBrainAgeCorrected.Rda")

@@

ggplot(brain_age_df_followup, aes(x=.pred)) +
  geom_histogram()

@@

ggplot(as.data.frame(brain_age_corrected_df), aes(x=corrected_pred)) +
  geom_histogram()

ggplot(as.data.frame(brain_age_corrected_df_followup), aes(x=corrected_pred)) +
  geom_histogram()
```
